My title

### 2024-02-12 starter_folder-main 4/paper/paper.qmd
added another figure but needs to be fixed

>>>>

library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)

# Define the path to your Excel file
file_path <- "/Users/michaelfang/Downloads/SCF_AER_submit.xlsx" # Update with the actual path to your Excel file

# Read the "Data for Figure 9" sheet from the Excel file, starting from the second row
data <- read_excel(file_path, sheet = "Data for Figure 9", skip = 4)

# Reshape the data: create two columns for grid log income and EMG (ML) PDF, with corresponding years
data_long <- data %>%
  pivot_longer(
    cols = c(`...1`, `...3`),
    names_to = "Year",
    values_to = "GridLogIncome"
  ) %>%
  pivot_longer(
    cols = c(`2016`, `1989`),
    names_to = "Temp",
    values_to = "EMG_ML_PDF"
  ) %>%
  filter(Year != Temp) %>%
  mutate(Year = ifelse(Year == "...1", "2016", "1989")) %>%
  select(-Temp)

# Plot the data
ggplot(data_long, aes(x = GridLogIncome, y = EMG_ML_PDF, color = Year)) +
  geom_line() +
  labs(title = "Comparison of Income Distribution for 1989 and 2016",
       x = "Log Household Income",
       y = "Density") +
  theme_minimal() +
  scale_color_manual(values = c("2016" = "blue", "1989" = "red"))
```
